Notebook with AMP-AD RNA-seq network analysis results

### 2020-01-03 manuscript.Rmd
add plots

Show overlap between AD and non AD (Figure SXF)
```{r}
AMPAD::compareADtoNonADmods(aggModsNew,
                            aggModsNonAdNew)

@@

```{r}
targetedGeneSets <- AMPAD::collateEnrichmentSets()
```

@@

>>>>

Show overlap between AD and non AD (Figure S2A)
```{r}
AMPAD::compareADtoNonADmods(aggModsNew,
                            aggModsNonAdNew)

@@

```{r}
targetedEnrichment <- AMPAD::run_full_enrichment_suite()
```

@@

Plot from Figure S2B

```{r}
dummyDf <- targetedEnrichment$cell2
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
#dummyDf <- dplyr::filter(targetedEnrichment$cell,adj.pval<=0.05)
dummyDf <- dplyr::left_join(dummyDf,modMeta)

g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='Lake et al. Cell Type Signature')
g
```

Plot for figure S6B

```{r}
dummyDf <- targetedEnrichment$scz
dummyDf <- dplyr::filter(dummyDf,category == 'yellow' | category == 'red' | category == 'blue' | category == 'lightyellow' | category == 'greenyellow' | category == 'cyan' | category == 'grey60')
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
#dummyDf <- dplyr::filter(targetedEnrichment$cell,adj.pval<=0.05)
dummyDf <- dplyr::left_join(dummyDf,modMeta)

g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='CommonMind Differentially Expressed Module')
g
```

plot from figure S6C

```{r}
dummyDf <- targetedEnrichment$mssm2
dummyDf <- dplyr::filter(dummyDf,category == 'Yellow' | category == 'Pink' | category == 'Gray.1' | category == 'Seashell' | category == 'Red.3' | category == 'Green.yellow' | category == 'Red' | category == 'Gold.2' | category == 'Tan' | category == 'Gold.3' | category == 'Light.yellow' | category == 'Brown.2' | category == 'Dark.cyan' | category == 'Khaki' | category == 'Grey.60' | category == 'Purple' | category == 'Green.4' | category == 'Honey.dew' | category == 'Red.2' | category == 'Beige')
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
#dummyDf <- dplyr::filter(targetedEnrichment$cell,adj.pval<=0.05)
dummyDf <- dplyr::left_join(dummyDf,modMeta)
g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='Zhang et al. Module')
g
```

Plot from figure 1D

```{r}
dummyDf <- targetedEnrichment$ad
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
dummyDf <- dplyr::left_join(dummyDf,modMeta)
#dummyDf$ModuleBrainRegion <- factor(dummyDf$ModuleBrainRegion,levels = unique(dummyDf$ModuleBrainRegion))
dummyDf$category <- factor(dummyDf$category,
                           levels = rev(c('genecards',
                                       'pantherPresenilin',
                                       'dbgap',
                                       'igap',
                                       'jensenDisease',
                                       'omimExpanded',
                                       'biocarta',
                                       'wikipathwaysMouse',
                                       'wikipathwaysHuman',
                                       'pantherAmyloid',
                                       'kegg',                                       
                                       'omim',
                                       'Nominated_targets',
                                       'MSSM',
                                       'Mayo_simple',
                                       'Mayo_comprehensive',
                                       'Emory',
                                       'Columbia_Broad_Rush_m109')))
g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='AD Signature')
g

plot from figure 4D

```{r}
dummyDf <- dplyr::filter(targetedEnrichment$degMeta,adj.pval<=0.05)
dummyDf <- dplyr::filter(dummyDf,category == 'ad.control.FEMALE.random.DOWN' |
                           category == 'ad.control.FEMALE.random.UP' | 
                           category == 'ad.control.MALE.random.DOWN' | 
                           category == 'ad.control.MALE.random.UP')
dummyDf$adj.pval[dummyDf$adj.pval==0] = 10^-300
dummyDf$category <- gsub('ad\\.control\\.FEMALE\\.random\\.DOWN','Female, Down',dummyDf$category)
dummyDf$category <- gsub('ad\\.control\\.MALE\\.random\\.DOWN','Male, Down',dummyDf$category)
dummyDf$category <- gsub('ad\\.control\\.FEMALE\\.random\\.UP','Female, Up',dummyDf$category)
dummyDf$category <- gsub('ad\\.control\\.MALE\\.random\\.UP','Male, Up',dummyDf$category)
dummyDf <- dplyr::left_join(dummyDf,modMeta)

g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='DEG Sex Specific Meta Analysis')
g
